---
title: "Crossfit Data"
output: github_document
---

```{r}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, comment="")
```

```{r}
library(kerasformula)
log_odds <- function(x, divide_by=100, scale=0.99){
  p <- scale*x/divide_by
  log(p/(1-p))
}
```

Below find publically-available data from the Crossfit annual open, an amateur athletics competition consisting of five workouts each year. "Rx", as in "perscription", denotes the heaviest weights and most complex movements. In this analysis, we restrict the predictors to height, weight, age, region, and performance in the first of the five rounds. We also restrict analysis who did all five rounds "Rx" and reported that other data. The analysis is repeated for men and women and 2017 and 2018.

# Men 2018 Competition

```{r}
Rx <- read.csv("Men_Rx_2018.csv")
colnames(Rx) <- gsub("[[:punct:]]", "", colnames(Rx))    # forgetmenot
colnames(Rx) <- tolower(colnames(Rx))
colnames(Rx) <- gsub("x18", "open", colnames(Rx))

Rx_tmp <- dplyr::select(Rx, heightm, weightkg, age, regionname, open1percentile, overallpercentile)
Rx_complete <- Rx_tmp[complete.cases(Rx_tmp), ]
dim(Rx_complete)
head(Rx_complete)

Rx_kms_out <- kms(overallpercentile ~ ., 
                  Rx_complete, seed=777, Nepochs=5, 
                  validation_split = 0, pTraining = 0.9)
Rx_kms_out$R2_predictions
Rx_kms_out$cor_kendals^2   # R^2 kendalls
Rx_kms_out$MSE_predictions
Rx_kms_out$MAE_predictions

```

# Men 2017 Competition

```{r}
Rx <- read.csv("Men_Rx_2017.csv")
colnames(Rx) <- gsub("[[:punct:]]", "", colnames(Rx))    # forgetmenot
colnames(Rx) <- tolower(colnames(Rx))
colnames(Rx) <- gsub("x17", "open", colnames(Rx))

Rx_tmp <- dplyr::select(Rx, heightm, weightkg, age, regionname, open1percentile, overallpercentile)
Rx_complete <- Rx_tmp[complete.cases(Rx_tmp), ]
dim(Rx_complete)

Rx_kms_out <- kms(overallpercentile ~ ., 
                  Rx_complete, seed=777, Nepochs=5, 
                  validation_split = 0, pTraining = 0.9)
Rx_kms_out$R2_predictions
Rx_kms_out$cor_kendals^2   # R^2 kendalls
Rx_kms_out$MSE_predictions
Rx_kms_out$MAE_predictions

```

# Women 2018 Competition

```{r}
Rx <- read.csv("Women_Rx_2018.csv")
colnames(Rx) <- gsub("[[:punct:]]", "", colnames(Rx))    # forgetmenot
colnames(Rx) <- tolower(colnames(Rx))
colnames(Rx) <- gsub("x18", "open", colnames(Rx))

Rx_tmp <- dplyr::select(Rx, heightm, weightkg, age, regionname, open1percentile, overallpercentile)
Rx_complete <- Rx_tmp[complete.cases(Rx_tmp), ]
dim(Rx_complete)

Rx_kms_out <- kms(overallpercentile ~ ., 
                  Rx_complete, seed=777, Nepochs=5, 
                  validation_split = 0, pTraining = 0.9)

Rx_kms_out$R2_predictions
Rx_kms_out$cor_kendals^2   # R^2 kendalls
Rx_kms_out$MSE_predictions
Rx_kms_out$MAE_predictions
```

# Women 2017

```{r}

Rx <- read.csv("Women_Rx_2017.csv")
colnames(Rx) <- gsub("[[:punct:]]", "", colnames(Rx))    # forgetmenot
colnames(Rx) <- tolower(colnames(Rx))
colnames(Rx) <- gsub("x17", "open", colnames(Rx))

Rx_tmp <- dplyr::select(Rx, heightm, weightkg, age, regionname, open1percentile, overallpercentile)
Rx_complete <- Rx_tmp[complete.cases(Rx_tmp), ]
dim(Rx_complete)

Rx_kms_out <- kms(overallpercentile ~ ., 
                  Rx_complete, seed=777, Nepochs=5, 
                  validation_split = 0, pTraining = 0.9)

Rx_kms_out$R2_predictions
Rx_kms_out$cor_kendals^2   # R^2 kendalls
Rx_kms_out$MSE_predictions
Rx_kms_out$MAE_predictions

```


